Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Mention PV in discussion

At a high level, the difference between these two schemes is in the number of mappings that must be
kept secret in order to ensure ballot secrecy. In \term{Scantegrity}, Table R has one mapping to Table Q
and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
But in \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
voters and tallies, respectively, without revealing the inner mapping. In some ways, \term{Helios}'s
approach accomplishes the same goals as \emph{but} is implemented as an antithesis of \term{Scantegrity}'s
Table system.

>>>>

At a high level, the difference between these two schemes is in the number of mappings that must be
kept secret in order to ensure ballot secrecy. In \term{Scantegrity}, Table R has one mapping to Table Q
and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
But in \term{\pv{}} and \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
voters and tallies, respectively, without revealing the inner mapping. While accomplishing the same
goals as \term{Scantegrity}'s Table system, this approach is in some ways its antithesis.
